Report on Late Winter2013 Production: Image Differencing

### 2013-03-29 W13report.tex
Small change to WCS section

\subsection{Astrometric Registration \label{subsec-astrom}}
The original plan for this production was to use the single deep exposures (v6866600) as 
inputs to the coadd process, to exercise use of the coadd repository.  As 
such we warped the exposures to coadd patches for use in the image difference
task.  The register task was unable to solve a differential WCS between the coadd
and science {\tt calexp} because in coadds, the parent WCS is for the entire {\tt tract}.
Each coadd {\tt patch} thus has a CRPIX at the center of the {\tt tract}, which is
typically off the {\tt patch} image.  TAN--SIP is unable to perform in this circumstance,
as it expands its polynomials around the CRPIX.  To get around this 
we tried re--solving the coadd patches using a TAN--SIP solution that was solved from
scratch.  This worked fairly will part of the time,
yielding residuals in the 40--100 mas range, compared to the 250 mas previously.  However,
as we did not understand the origin of these problems, and there were legitimate bugs
in meas\_astrom  that were uncovered as a result of this investigation, we reverted to
using the deep {\tt calexp} as the template directly; the direct {\tt calexp} to {\tt calexp} 
registration yielded residuals in the range of 5--7 mas (well, its 0.02 pixels).

>>>>

\subsection{Astrometric Registration \label{subsec-astrom}}
The original plan for this production was to use the single deep exposures (v6866600) as 
inputs to the coadd process, to exercise use of the coadd repository.  As 
such we warped the exposures to coadd patches for use in the image difference
task.  The register task was unable to solve a differential WCS between the coadd
and science {\tt calexp} because in coadds, the parent WCS is for the entire {\tt tract}.
Each coadd {\tt patch} thus has a CRPIX at the center of the {\tt tract}, which is
typically off the {\tt patch} image.  TAN--SIP is unable to perform in this circumstance,
as it expands its polynomials around the CRPIX.  To get around this 
we tried re--solving the coadd patches using a TAN--SIP solution that was solved from
scratch.  This worked fairly will part of the time,
yielding residuals in the 40--100 mas range, compared to the 250 mas previously.  However,
as we did not understand the origin of these problems, and there were legitimate bugs
in meas\_astrom  that were uncovered as a result of this investigation, we reverted to
using the deep {\tt calexp} as the template directly; the direct deep {\tt calexp} to science {\tt calexp} 
registration typically yielded residuals in the range of 4--5 mas.
